---
title: ""
output: 
  html_document:
    keep_md: yes
editor_options: 
  chunk_output_type: console
---

# ChooseRef
Functions for the Durbecq et al. paper (in prep) about ecosystem references


### How to install the package?

If not yet installed, you should install `devtools`:

```{r eval=FALSE}
install.packages(devtools)
```

Load `devtools:

```{r eval=FALSE}
library(devtools) 
```

Install package `ChoosRef`:

```{r eval=FALSE}
install_github("RenaudJau/ChooseRef")
```

And load it:

```{r}
library(ChooseRef)
```


### How to use the functions?

Here is an example with the `dune` dataset from `vegan` package :

```{r message=FALSE}
library(vegan)
data("dune") #downloading of dune data (cf vegan)
data("dune.env") #downloading of dune.env data (cf vegan)
# keeping only the numeric variables :
dune.env <- data.frame(A1 = dune.env$A1, 
                       Moisture =  as.numeric(as.vector(dune.env$Moisture)),
                       Manure = as.numeric(as.vector(dune.env$Manure)))
                                          
# Creating a vector indicating which plots are the potential references and which ones are the restored sites
sites <- factor(c(rep("Rest",5),rep("Ref",15)))
# Creating a vector with the plot names
sites_names <- paste(sites,c(1:5,1:15))
#Poviding names to rows (useful for the outputs)
row.names(dune.env) <- sites_names
row.names(dune) <- sites_names
dune.envRest <- dune.env[sites=="Rest",]
dune.envRef <- dune.env[sites=="Ref",]
```

So your data.frame should look something like:

* Your restoration sites environmental data:
```{r echo=FALSE}
library(knitr)
kable(data.frame(dune.envRest))
```

* Your potential references environmental data:
```{r echo=FALSE}
kable(data.frame(dune.envRef))
```

#### Calculating reference dissimilarities

```{r}
Distances <- DissRef3(RELEVES = dune.envRest, REF = dune.envRef, METHOD = "euclidean", DUPLICATES = FALSE)
Distances
```

#### Plotting reference dissimilarities

```{r warning=FALSE}
Diss_Ref_Plot(RELEVES = dune.envRest, REF = dune.envRef, DISTANCES = Distances, LINK_NUMBER = "N_REF", N_REF = 3)
```

